Instructions for COLING-2020 Proceedings

### 2020-06-26 Paper/main.tex
Commit

\section{Related Work}
\label{sec:related}
\subsection{Stefanos}
Datasets: 
\begin{enumarate}
  \item DENS: A Dataset for Multi-class Emotion Analysis:By finetuning the pre-trained uncased BERT-large to a multi-class passage classification task they achieved a micro-F1 score of 60.4\%. 
  \item 
\end{enumarate}

>>>>

\section{Related Work}
\label{sec:related}
\subsection{Stefanos}
Datasets:

DENS: A Dataset for Multi-class Emotion Analysis:By finetuning the pre-trained uncased BERT-large to a multi-class passage classification task they achieved a micro-F1 score of 60.4\%.
